%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Vice Instructor (part-time)} % Job title
    {KryptoCamp} % Organization
    {Taipei City, Taiwan} % Location
    {Jan. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solved students blockchain development issues and corrected students' assignments}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Back End Team Lead} % Job title
    {CYR Digital Entertainment CO., LTD.} % Organization
    {Taipei City, Taiwan} % Location
    {Nov. 2020 - Dec 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed Event-Driven Architecture (Event Sourcing, CQRS, BFF, API Composition) and managed 300+ containers with k8s}
        \item {Implemented micro-services development and testing template which made developers focus on business logic development}
        \item {Provisioned an easily manageable infrastructure (Amazon AWS, Github) utilizing IaC (Terraform)}
        \item {Built fully automated CI/CD pipelines on Github Actions for containerized applications using Docker, AWS ECR, ArgoCD}
        \item {Deployed a centralized logging environment (EFK, Elasticsearch, Fluentd, Kibana) which gather log data from Docker containers}
        \item {Deployed a centralized monitoring environment (Prometheus, Grafana) which gather system metrics as well as containers run-time metrics}
        \item {Deployed a centralized tracing environment (Istio, Zipkin, Jaeger) which gather micro-services requests}
        \item {Developed C\#, Javascript Client SDK which made front-end team focus on UI/UX}
        \item {led 3 back-end engineers, 2 web front-end engineers, 2 QA, ensuring feature delivered on time}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {CYR Digital Entertainment CO., LTD.} % Organization
    {Taipei City, Taiwan} % Location
    {Dec. 2019 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in board game back-end development which helped the company get 1m USD investment}
        \item {Implemented a distributed stress client with 5000+ anonymity}
        \item {Evaluated mobile app project features using flutter development which reduced two manpower}
        \item {Developed an instant messaging system with a global gambling company}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {SHOW U FASHION TECHNOLOGY CO., LTD.} % Organization
    {Taipei City, Taiwan} % Location
    {Dec. 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated back-end framework from egg.js to nest.js made it more maintainable and developed 80\% features (payment, video call, IM, ...etc.)}
        \item {Built and Deployed overall service infrastructure utilizing Docker container and several AWS stack (Lambda, APIGateway, EC2, ECS, Route 53, S3, CloudFront, RDS, Elasticache, IAM, Elastic Beanstalk, SQS, SNS, SES, SMS)}
        \item {Introduced Typescript into React Native mobile app development made it maintainable and developed 40\% features }
        \item {Introduced Code Push technology which made app development can adapt to marketing change}
        \item {Collaborated with NeuHelium AI team to build a women's goods recommended system}
        \item {Participated in Beijing product press conference, responsible for ensuring app DEMO smoothly}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {BROCAS CO., LTD.} % Organization
    {Taipei City, Taiwan} % Location
    {Aug. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and Maintained 3 projects back-end server using Node.js web framework Koa, Express}
        \item {Developed and Maintained admin console UI using React and Vue}
        \item {Wrote a product back-end test cases, ensuring coverage above 90\%}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Software Developer} % Job title
    {International Integrated Systems, Inc.} % Organization
    {Taipei City, Taiwan} % Location
    {Feb. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and Developed bank system using J2EE Technologies}
      \end{cvitems}
    }

%---------------------------------------------------------
 
\end{cventries}
